---
title: "Sample Data Analysis with faudmutils Package"
author: "Michael Crawford"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Sample Data Analysis with faudmutils Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

This is a sample of how to use the **faudmutils** package.  
We will take a sample output file from a datamining request and load it into R.  
Then some basic statistical analysis wil be performed on the file.

First we need to load the relevant packages:

```{r}
library(knitr)
library(faudmutils)
library(RWeka)
suppressPackageStartupMessages(library(dplyr))
library(xtable)
library(agricolae)
```

Now we simply take our results file and pass it into mapKeys in order to get usable dataframe of the results.

First we are going to find the location of our datafile.  
*You will not need to do this step since you know the loaction of your file.  This is simply a way to identify the location of the sample data in your local R install*

```{r}
zipfile <- system.file("extdata","newreview-wordvector-output.zip",package="faudmutils")
```

zipfile now has the location of the zip file which contains the results of the data mining experiment.  Note that there is no reason to actually unzip the results.  R will grab the data directly out of the zipfile (How cool is that?)

Now we have what we need to do our initial mapping.  We need to call **mapKeys** from the **faudmutils** package.  
This will default to loading the data from the `output/normal/output2.arff` file in the zipfile

```{r}
df <- mapKeys(zipfile)
```

Now everything has been mapped to a human readable format!!

```{r}
unique(df$Learner)  # Learner names are now human readible
unique(df$Dataset) #  No more dataset numbers
```

While the Dataset column is surely much better than numbers, in our particular case we can make it even better.  
since each dataset represents a domain we will change those to even better names with the 
[revalue](http://www.inside-r.org/packages/cran/plyr/docs/revalue) function from the plyr package.

```{r}
df$Dataset <- plyr::revalue(df$Dataset,c("reviewSpamData-string-hotel.arff"="hotel",
                                           "reviewSpamData-string-restaurant.arff"="restraunt",
                                           "reviewSpamData-string-doctor.arff"="doctor"))
table(df$Dataset)
```



Now lets use the [dplyr package](https://cran.rstudio.com/web/packages/dplyr/vignettes/introduction.html)  to sample out 10
random rows and select a few key columns to examine.  We then pass that into the 
[kable function](http://www.inside-r.org/packages/cran/knitr/docs/kable) which produces a nice stylized output.

```{r}
sampledDF <- sample_n(df,10)
sampledDF <- select(sampledDF,Dataset,SamplingTechnique,WordsToKeep,Learner,AUC)
kable(sampledDF,row.names = FALSE)
```

Ok so we have our data now what?  Let's do some analysis!!!

First we should probably do an ANOVA test.  Well this is super easy in R.

```{r}
df.aov <- aov(AUC ~ Dataset*Learner,df)
summary(df.aov)
```

Well that looks ok, but what if we instead want a nice table.  well we can use the 
[xtable](https://cran.r-project.org/web/packages/xtable/xtable.pdf) package.


```{r results='asis'}
print(xtable(df.aov),type="html")
```

You could even generate latex (you do use latex don't you?) for your report.

```{r}
print(xtable(df.aov),type="latex")
```

If you add a file option to the print command (` print(xtable(df.aov),type="latex",file="anovatable.tex")`) it will write the latex directly to a file which you can
include in your latex report with `\input{filename.tex}` command.


Great but what about those Tukey test tables?  Well we have a few functions to help you out there as well.

First lets do a Tukey HSD test of Learner across all datasets.  
We will use the [HSD.test](http://www.inside-r.org/packages/cran/agricolae/docs/HSD.test) 
function from the agricolae package.

```{r}
HSD.test(df.aov,"Learner",console = TRUE)
```

While that works it isn't very pretty, so we have done the work for you in reformating this in a presentable format
with the HSDTable method from our **faudmutils* package.

```{r, results='asis'}
HSDTable(df.aov)
```

But we only wanted to do it by learner.  No problem...

```{r, results='asis'}
HSDTable(df.aov,which="Learner")
```


